### 2016-08-23 numerics.tex
Add a small intro paragraph to the numerics section (review 3, point 24)

Floating-point numbers in SymPy are implemented by the \texttt{Float} class,
which represents an arbitrary-precision binary floating-point number by
storing its value and precision (in bits). This representation is distinct
from the Python built-in \texttt{float} type, which is a wrapper around
machine \texttt{double} types and uses a fixed precision (53-bit).

>>>>

While SymPy primarily focuses on symbolics, it is impossible to have a
complete symbolic system without the ability to numerically evaluate
expressions. Many operations directly use numerical evaluation, such as
plotting a function, or solving an equation numerically. Beyond this, certain
purely symbolic operations require numerical evaluation to effectively
compute. For instance, determining the truth value of $e + 1 > \pi$ is most
conveniently done by numerically evaluating both sides of the inequality and
checking which is larger.

\subsection{Floating-Point Numbers}
Floating-point numbers in SymPy are implemented by the \texttt{Float} class,
which represents an arbitrary-precision binary floating-point number by
storing its value and precision (in bits). This representation is distinct
from the Python built-in \texttt{float} type, which is a wrapper around
machine \texttt{double} types and uses a fixed precision (53-bit).
